\chapter*{Abstract}
\noindent
Along with fast development of human society, it emerges lots of revolution in various territories. The development of traditional regular calculator is just one of them that is under great challenge. People are not only satisfied with the default process to obtain results from using traditional regular calculator, but desire for a more convenient and efficient solution. The widely used solution based on regular calculator with its design of scientific mode, therefore attracts lots of people’s attention. Hence, how to validate the scientific number and the scientific mathematical calculation and decent user-device interaction experience become crucial topic for calculator designer. 
To better serve to this case study here, a simple but efficient calculator design with several specific scientific calculation function with number (PI), is used to model and verify a scientific calculator. The entire case study report is organized as: after introduction, the Brief Description regarding problem 1 gives the basic background regarding the assigned number; Chapter of Interview provides the Question and Answer interview session and the interview analysis; Chapter 4, User Personas, the two interviewees are introduced and answers to problem 3 are provided; To analyze the problem domain, the concepts relationship and class diagram are provided in chapter 5 for problem 4; Problem 5 gives all the use cases and describes carefully for each. Besides, sequence diagram and activity diagram are provided for further description.

\\
%\vspace{8mm}
\begin{spacing}{1.0} 
\end{spacing} 
\noindent
{\textbf{Keywords: calculator, number, function, PI} }




